{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Complete a first round of proofreading.

\textbf{Features Selections.} We used the fast Histogram of Oriented
Gradients (fHoG)\cite{felzenszwalb2010object} and
color-naming\cite{van2009learning} features to learn target and
background models. $R_{t}^{L}$ uses both fHoG and color features as it
covers a large ROI where fHoG features may not be reliable alone. On
the other hand, $R_{t}^{S}$ is assigned only fHoG features as it
covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features
as it is assigned lower template size, yielding space to exploit two
feature modalities. We note that we use the same features for the {\it
  E}nKCF2 tracker.

@@

{\it YoungWoo: End of 04/30/17}

In precision, we rank the trackers based on the precision numbers at
20 pixels. The success rate metric evaluates the overlap between the
ground truth and tracking output. The intersection-to-union ratio of
two regions over the frames of one sequence. Finally, we count the
number of frames with overlap larger than the success rate threshold
and divide it by the number of frames. We compare our tracker to some
other high-speed ($\geq$300 fps) state-of-the-art trackers including
KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting},
STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset. The {\it E}nKCF tracker outperforms the other methods in
high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
the same dataset although it is $10$-$20$ times faster than these
trackers. On the other hand, the {\it E}nKCF does a decent job on
approximating the scale of the target in highly efficient manner. This
is proved by the fact that it ranks third best tracker in terms of
\textit{area under curve} (AUC) value for the success rate plot. It
outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
metric. Interestingly, it performs even better than most of the low
speed trackers. For instance, it outperforms Struct and DSST by $5\%$
and $10\%$ while running at more than $30$ and $10$ times larger
operation rate.

>>>>

\textbf{Features Selections.} As each of three KCFs in the {\it E}nKCF
has different goals to accomplish, we used different features for each
of them. In particular, the translation filter, $R_{t}^{L}$, uses both
the fast Histograms of Oriented Gradients
(fHoG)\cite{felzenszwalb2010object} and
color-naming\cite{van2009learning} features to learn the background
around the target more effectively. In fact we empirically found fHoG
only didn't work well to cover the larger ROI. Another translation
filter, $R_{t}^{S}$, used fHoG features only. The scale filter,
$R_{s}$ used both fHoG and color features to learn the scale change
more accurately.

@@

{\it Burak: What do mean by the following sentence? We had graphs
  about precision, but I don't see any tables or anything else to rank
  the algorithms based on the precision at 20 pixels.}

In precision, we rank the trackers based on the precision numbers at
20 pixels.

The success rate metric counts how many outputs from a tracking
algorithm successfully overlap with those of the ground truth greater
than a given threshold. The overlap is specifically computed by the
Intersection-Over-Union (IoU) between a tracking output and that of
the ground truth. Given the number of the correct frames based an IoU
threshod, the success rate is the ratio of the correct frames to the
number of the total frames for testing.

{\it Burak: After you remove some of the trackers, replace that number
  with ``some'' at the below as well as removing their names from the
  following paragraph.}

We compare our tracker to some other high-speed ($\geq$300 fps)
state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset.

{\it Burak: I will re-write the text at below after you clean up the graphs.}

{\it E}nKCF outperformed other, high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision metric whereas it is only $5\%$
worse than SAMF, DSST and Struck on the same dataset although it is
$10$-$20$ times faster than these trackers. On the other hand, the
{\it E}nKCF does a decent job on approximating the scale of the target
in highly efficient manner. This is proved by the fact that it ranks
third best tracker in terms of \textit{area under curve} (AUC) value
for the success rate plot. It outperforms the high speed trackers by
about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even
better than most of the low speed trackers. For instance, it
outperforms Struct and DSST by $5\%$ and $10\%$ while running at more
than $30$ and $10$ times larger operation rate.
